Estimating individual subjective values of emotion regulation strategies

### 2022-02-23 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
lay beliefs
Update Manuscript_ERED_Stage1.Rmd
added ACS and implicit theories

*Implicit theories of willpower.*

@@

>>>>

*Implicit Theories Questionnaire.*
Implicit theories of willpower in emotional control are assessed using the Implicit Theories Questionnaire of @Bernecker2017.
4 items such as "Having to control a strong emotion makes you exhausted and you are less able to manage your feelings right afterwards." are rated on a 6-point scale ranging from 1 (fully agree) to 6 (do not agree at all).
The questionnaire showed an internal consistency of Cronbach's $\alpha=.87$[@Bernecker2017].

@@

*Attentional Control Scale.*
Attentional control is measured using the Attentional Control Scale (ACS)[@Derryberry2002] with items such as "My concentration is good even if there is music in the room around me".
The 20 items are rated on a 4-point scale ranging from 1 (almost never) to 4 (always).
An internal consistency of Cronbach's $\alpha=.88$ was reported [@Derryberry2002].
